The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-12-29 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated Section 3

\textcolor{blue}{Within the \emph{TestIdeals} package, the functions \texttt{testIdeal} and \texttt{FPureModule} are used to compute the test ideals of $f$ at different parameters.
By comparing test ideals of $f$ at different parameters, we can decide  whether $t$ is the $F$-pure threshold of $f$. 
Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}

\noindent \textcolor{red}{Another possibility:}

>>>>

% \textcolor{blue}{Within the \emph{TestIdeals} package, the functions \texttt{testIdeal} and \texttt{FPureModule} are used to compute the test ideals of $f$ at different parameters.
% By comparing test ideals of $f$ at different parameters, we can decide  whether $t$ is the $F$-pure threshold of $f$. 
% Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}
% 
% \noindent \textcolor{red}{Another possibility:}
